Universal relations after GW170817

### 2018-12-20 paper/bin-love-after-gw170817.tex
fixed figure 2

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
Unfortunately, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.eps}
\end{center}
\caption{
Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year.
It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple) for Voyager and on.
Note there is no simulated populations of events under the O2 design sensitivity - due to there only being a single event during the observing period.
These results are further tabulated in Table~\ref{tab:variances}.
}
\label{fig:stackedFisher}
\end{figure}

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{EoSs.eps}
\end{center}
\caption{
Small representative sets of the constrained (left) and unconstrained (right) EoSs used in this analysis. 
The constrained EoSs were populated by randomly selecting 100 posterior samples obtained from the GW170817 90\% credible level shown in cyan~\cite{LIGO:posterior}.
Additionally, 100 unconstrained EoSs were generated by randomly sampling spectral coefficients of physically valid EoSs, with no further constrained applied.
The following constraints were also applied to both sets of EoSs: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
}
\label{fig:eos}
\end{figure}

>>>>

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
Unfortunately, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.eps}
\end{center}
\caption{
Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year.
It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.
Note there is no simulated populations of events under the O2 design sensitivity - due to there only being a single event during the observing period.
These results are further tabulated in Table~\ref{tab:variances}.
}
\label{fig:stackedFisher}
\end{figure}

@@

\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{EoSs.eps}
\end{center}
\caption{
Small representative sets of the unconstrained (dotted) and constrained (solid) EoSs used in this analysis. 
The constrained EoSs were populated by randomly selecting 100 posterior samples obtained from the GW170817 90\% credible level shown in cyan~\cite{LIGO:posterior}.
Additionally, 100 unconstrained EoSs were generated by randomly sampling spectral coefficients of physically valid EoSs, with no further constrained applied.
The following constraints were also applied to both sets of EoSs: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
Finally, the high density core EoSs generated above were stitched to the low-density crust EoS of SLy~\cite{Douchin:2001sv} at $\rho_{\text{stitch}}=1.3 \times 10^{14} \text{ g/cm}^3$.
}
\label{fig:eos}
\end{figure}
